Annotation exploration for SCPCP000006

### 2024-10-30 analyses/cell-type-wilms-tumor-06/notebook/07_annotation_Across_Samples_exploration.Rmd
Update analyses/cell-type-wilms-tumor-06/notebook/07_annotation_Across_Samples_exploration.Rmd
Co-authored-by: Stephanie Spielman <stephanie.spielman@gmail.com>

```{r packages, message=FALSE, warning=FALSE}
library(Seurat)
library(tidyverse)
library(tidyr)
library(patchwork)
library(DT)
```

@@

We extracted from the pre-processed and labeled `Seurat` object (that is the output of `06_infercnv_HMM-i3_SCPCS000169_reference-both.rds` saved in the `results` directory)
the following information per cell:

>>>>

```{r packages, message=FALSE, warning=FALSE}
library(Seurat)
library(tidyverse)
library(patchwork)
library(DT)
```

@@

We extracted from the pre-processed and labeled `Seurat` object from `results/{sample_id}/06_infercnv_HMM-i3_SCPCS000169_reference-both.rds`.
the following information per cell:
